OCMu64: a solver for One-sided Crossing Minimization

### 2024-06-20 tex/description.tex
More minor changes.

\section{Methods}
\subsection{Reductions}
\subparagraph{Fixed pairs}
We give a much stronger version of \cref{lem:weak}. In fact, \cref{lem:sfp} is the strongest
generalization possible when only considering $u, v$ themselves (see \cref{rem:strongest}).
\begin{definition}
    We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have ${\sum_{a
    \leq b} \bar u(a) \geq \sum_{a \leq b} \bar v(a)}$, and at least one of these inequalities
    is strict. This implies $r(u, v) {<} 0$.
\end{definition}
\begin{lemma}[Strongly fixed pair]\label{lem:sfp} When $u, v$ is a strongly fixed pair,
    then for any $w: A\to \mathbb R^{\geq 0}$ we have $r(w, \bar v) \leq r(w, \bar u)$.
\end{lemma}
\begin{proof}
    Consider the least element $a_0 \in A$ such that $\bar u(a_0) \neq
    \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Now consider the transformation of
    $\bar u$ which ``moves'' $\delta := \bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its
    successor $a_1 \in A$, and call this transformed function $\bar u'$. Then
    \[
        r(w, \bar u') = r(w, \bar u) - \delta w(a_0) - \delta w(a_1) \leq r(w, \bar u).
    \]
    Since $\bar v$ is obtained from $\bar u$ by a sequence of such transformations,
    the inequality follows.
\end{proof}
\begin{lemma}
    If $(u, v)$ is strongly fixed, then $u \b v$.
\end{lemma}
\begin{proof}
    Suppose towards a contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
    solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, \bar u) = W_v / W_u r(X,
    u) \leq 0$. But then $c(X, u, v) < c(X, v, u)\leq c(v, X, u)$, which
    contradicts $(v,X,u)$ being optimal.
\end{proof}

\begin{remark}
    Consider $u \neq v$ from the original, unweighted problem, taking only values $0, 1$. Let 
    $n = |N(u)|, m = |N(v)|$, and consider both as ordered lists. Then $u, v$ are strongly
    fixed if and only if for all $0 \leq i < n$,
    \[
        N(u)_i \leq N(v)_{\lfloor i\cdot m/n \rfloor},
    \]
    or equivalently for all $0 \leq j < m$, $N(u)_{\lceil j\cdot n/m \rceil} \leq N(v)_j$.
\end{remark}

\begin{remark}\label{rem:strongest}
    Suppose that $u \neq v$ are not strongly fixed, and let $b \in A$ be some element such
    that $\sum_{a \leq b} \bar u(a) > \sum_{a \leq b} \bar v(a)$. By taking $X: A \to \mathbb
    R^{\geq 0}$ some function which assigns very high
    weight to $b$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, showing that
    \cref{lem:sfp} is optimal.
\end{remark}
Although such a function $X$ may exist in theory, it does
not have to exist in the actual set $B$, motivating the following definition.

>>>>

\section{Methods}
\subsection{Reductions}
\subparagraph{Fixed pairs}
We give a much stronger version of \cref{lem:weak}. In fact, \cref{lem:sfp} is the strongest
generalization possible when only considering $u, v$ themselves (see \cref{rem:strongest}).
\begin{definition}[Strongly fixed pair]
    We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have ${\sum_{a
    \leq b} \bar u(a) \geq \sum_{a \leq b} \bar v(a)}$, and at least one of these inequalities
    is strict. This implies $r(u, v) < 0$.
\end{definition}
\begin{lemma}\label{lem:sfp} When $u, v$ is a strongly fixed pair,
    then for any $w: A\to \mathbb R^{\geq 0}$ we have 
    \[
        r(w, \bar v) \leq r(w, \bar u).
    \]
\end{lemma}
\begin{proof}
    Consider the least element $a_0 \in A$ such that $\bar u(a_0) \neq
    \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Now consider the transformation of
    $\bar u$ which ``moves'' $\delta := \bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its
    successor $a_1 \in A$, and call this transformed function $\bar u'$. Then
    \[
        r(w, \bar u') = r(w, \bar u) - \delta w(a_0) - \delta w(a_1) \leq r(w, \bar u).
    \]
    Since $\bar v$ is obtained from $\bar u$ by a sequence of such transformations,
    the inequality follows.
\end{proof}
\begin{lemma}
    If $(u, v)$ is strongly fixed, then $u \b v$.
\end{lemma}
\begin{proof}
    Suppose towards a contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
    solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, \bar u) = W_v / W_u \cdot
    r(X, u) \leq 0$. But then $c(X, u, v) < c(X, v, u)\leq c(v, X, u)$, which
    contradicts $(v,X,u)$ being optimal.
\end{proof}

\begin{remark}
    Consider $u \neq v$ from the original, unweighted problem, taking only values $0, 1$. Let 
    $n = |N(u)|, m = |N(v)|$, and consider both as ordered lists. Then $u, v$ are strongly
    fixed if and only if for all $0 \leq i < n$, $N(u)_i \leq N(v)_{\lfloor i\cdot m/n
    \rfloor}$, which is how we check in practice whether $u, v$ is strongly fixed.
\end{remark}

\begin{remark}\label{rem:strongest}
    Suppose that $u, v \in B$ with $\bar u \neq \bar v$ are not strongly fixed, and let $b \in
    A$ be some element such
    that $\sum_{a \leq b} \bar u(a) > \sum_{a \leq b} \bar v(a)$. By taking $X: A \to \mathbb
    R^{\geq 0}$ some function which assigns very high
    weight to $b$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, showing that
    \cref{lem:sfp} is optimal.
\end{remark}
Although such a function $X$ may exist in theory, it does
not have to exist in the actual set $B$, motivating the following definition.
